FTLR proof cases

### 2018-07-03 fully-abstract-comp/ftlr-proof-cases.tex
removed TODOs and added short disclaimer.
Fix non-expansiveness of stack, free stack and heap satisfaction, adapt step accounting throughout the paper to follow suit.

  The property for $\lrheap$, $\memSatFStack{\_,\_}{\_}$, $\memSatStack{\_,\_}{\_}$ follows from the downward closure of regions in the world, and the property for $(\_,\_,\_,\_) :_n W$ follows from those.
\end{proof}

\begin{lemma}[Properties of n-equality of worlds]
  \label{lem:n-equality-props}
  If $W_1 \nequal W_2$ then
  \begin{itemize}
  \item $\purePart{W_1} \nequal \purePart{W_2}$
  \item If $W_1' \future W_1$ then there exists a $W_2'$ such that $W_2' \nequal W_1'$ and $W_2' \future W_2$.
  \item If $W_1' \oplus W_1$ is defined, then there exists a $W_2' \nequal W_1'$ and $W_2' \oplus W_2$ is defined.
  \item If $W_1 = W_1' \oplus W_1''$ then there exist $W_2' \nequal W_1'$ and $W_2'' \nequal W_1''$ such that $W_2 = W_2' \oplus W_2''$.
  \end{itemize}
\end{lemma}
\begin{proof}
  Easy to prove by unfolding definitions and making unsurprising choices for existentially quantified worlds.
\end{proof}

\begin{lemma}[Non-expansiveness of relations]
  \label{lem:non-expansiveness}
  If $W \nequal W'$, then
  \begin{itemize}
  \item $\readCond{W} \nequal \readCond{W'}$.
  \item If $\stackReadCond{\lin,W} \nequal \stackReadCond{\lin,W'}$.
  \item If $\writeCond{\lin,W} \nequal \writeCond{\lin,W'}$.
  \item If $\stackWriteCond{\lin,W} \nequal \stackWriteCond{\lin,W'}$
  \item If $\xReadCond{W} \nequal \xReadCond{W'}$.
  \item $\lre(W) \nequal \lre(W')$.
  \item $\lrexj(W) \nequal \lrexj(W')$.
  \item If $\execCond{\lin,W} \nequal \execCond{\lin,W'}$.
  \item If $\lrvg{\trust}(W) \nequal \lrvg{\trust}(W')$.
  \item If $\lrrg{\trust}(W) \nequal \lrrg{\trust}(W')$.
  \item If $\memSatFStack{ms_\stk,\ms_T}{W}$, then $\memSatFStack{ms_\stk,\ms_T}{W'}$.
  \item If $\memSatStack{ms_\stk,\ms_T}{W}$, then $\memSatStack{ms_\stk,\ms_T}{W'}$.
  \item If $\npair{(\overline{\sigma},\ms_S,\ms_T)} \in \lrheap{\pwheap}(W)$, then $\npair{(\overline{\sigma},\ms_S,\ms_T)} \in \lrheap{\pwheap[W']}(W')$.
  \item $\memSat{(\ms_S,\stk,\ms_\stk,\ms_T)}{W}$ iff $\memSat{(\ms_S,\stk,\ms_\stk,\ms_T)}{W'}$.
  \item ...
  \end{itemize}
\end{lemma}
\begin{proof}
  The properties for $\readCond{}$, $\stackReadCond{}$, $\writeCond{}$, $\stackWriteCond{}$, $\xReadCond{}$ follow from the fact that these are defined to use the world only for comparing regions using $\nequal$, $\nsubeq$ and $\nsupeq$.

@@

  The property for $\lrv$ follows from the other properties, by definition, from Lemma~\ref{lem:n-equality-props}, non-expansiveness of regions \dominique{Is $\xi$ non-expansive/contractive/?}
  \lau{I believe it is at-least non-expansive and monotone as it is a morphism in the category of preordered c.o.f.e.'s.
    Do you also ``need'' it to be contractive?}
  TODO

@@

  The property for $\lrheap$, $\memSatFStack{\_,\_}{\_}$, $\memSatStack{\_,\_}{\_}$ and $(\_,\_,\_,\_) :_n W$ follows from the non-expansiveness of regions in the world. \dominique{and $\xi?$}
  TODO
\end{proof}

@@

  From $\npair{(\overline{\sigma},\ms_S',\ms_\var{T,heap})} \in \lrheap(W_M)(W_\var{heap})$, we get an
  $R_\ms : \dom(\activeReg{\pwheap[W_\var{heap}]}) \fun \MemSeg \times \MemSeg$,
  $\ms_\var{T,heap} = \biguplus_{r \in \dom(\activeReg{\pwheap[W_\var{heap}]})} \pi_2(R_\ms(r))$,
  $\ms_S = \biguplus_{r \in \dom(\activeReg{\pwheap[W_\var{heap}]})} \pi_1(R_\ms(r))$,
  $\exists R_W : \dom(\activeReg{\pwheap[W_\var{heap}]}) \fun \World\ldotp$
  $W_\var{heap} = \oplus_{r \in \dom(\activeReg{\pwheap[W_\var{heap}]})} R_W(r)$,
  $\forall r \in \activeReg{\pwheap[W_M]}$, we have that
  $\npair{R_\ms(r)} \in  \pwheap[W_\var{heap}](r).H \; \xi^{-1}(R_W(r))$.
  We also get an $R_\var{seal} : \dom(\activeReg{\pwheap}) \fun \powerset{\Seal}$ such that  $\biguplus_{r \in \dom(\activeReg{\pwheap})} R_\var{seal}(r)) \subseteq \overline{\sigma}$ and $\dom(\pwheap(r).H_\sigma) = R_\var{seal}(r)$.

  We have that $r \in \addressable{\lin, \pwheap} \subseteq
  \activeReg{\pwheap[W_\var{heap}]}$, so $\npair{R_\ms(r)} \in
  \pwheap[W_M](r).H \; \xi^{-1}(R_W(r))$.
  Because $\pwheap(r).H \nsubeq \stdreg{R(r),\gc}{\pur}.H$ and $W\oplus W_M$ is defined, it follows that
  also $\pwheap[W_M](r).H \nsubeq \stdreg{R(r),\gc}{\pur}.H$. This
  means that also $\npair{R_\ms(r)} \in
  H^{\mathrm{std}}_{R(r)}\; \xi^{-1}(R_W(r))$.

  From this, it follows that $\dom(R_\ms(r).1) = \dom(R_\ms(r).2) = R(r)$ and we get a $S : R(r) \fun \World$ with $\xi(\xi^{-1}(R_W(r))) = \oplus_{\aaddr \in R(r)} S(\aaddr)$ and $\forall \aaddr \in R(r),n' < n \ldotp \npair[n']{(\ms_S(\aaddr),\ms_T(\aaddr))} \in \lrv(S(\aaddr))$.

  Since $\aaddr \in R(r)$ and $n' < n$, we have that $\npair[n']{(\ms_S(\aaddr),\ms_T(\aaddr))} \in \lrv(S(\aaddr))$ and
  we can take $W_M' = W_r' \oplus W_{\var{heap}}' \oplus (W_{\var{stack}} \oplus W_{\var{free\_stack}})$ with $W_r' = \oplus_{\aaddr \in (R(r)\setminus \{\aaddr\})} S(\aaddr)$ and $W_\var{heap}' = \oplus_{r' \in (\dom(\activeReg{\pwheap[W_\var{heap}]})\setminus \{r\})} R_W(r')$, and get
  \begin{align*}
    S(\aaddr) \oplus W_M'
    &=S(\aaddr) \oplus (W_r' \oplus W_\var{heap}'\oplus (W_{\var{stack}} \oplus W_{\var{free\_stack}}))\\
    &=
    \oplus_{\aaddr \in R(r)} S(\aaddr) \oplus W_{\var{heap}}'\oplus (W_{\var{stack}} \oplus W_{\var{free\_stack}})\\
    &=
    \xi(\xi^{-1}(R_W(r))) \oplus W_\var{heap}'\oplus (W_{\var{stack}} \oplus W_{\var{free\_stack}})\\
    &=
    R_W(r) \oplus W_\var{heap}'\oplus (W_{\var{stack}} \oplus W_{\var{free\_stack}})\\
    &=
    \oplus_{r \in \dom(\activeReg{\pwheap[W_\var{heap}]})} R_W(r)\oplus (W_{\var{stack}} \oplus W_{\var{free\_stack}})\\
    &=
      W_\var{heap} \oplus (W_{\var{stack}} \oplus W_{\var{free\_stack}})\\
      &= W_M
  \end{align*}

@@

  We have that $\npair{(R_\ms(r).1\update{a}{0},R_\ms(r).2\update{a}{0})} \in \pwheap[W_\var{heap}](r).H \; \xi^{-1}(W_r')$ because $\pwheap[W_M](r)$ is address-stratified and $\pwheap[W_M](r).H \nsupeq \stdreg{R'(r),\gc}{\pur}.H$.

@@

  From $\memSatFStack{\ms_\stk,\ms_\var{T,free\_stack}}{W_{\var{free\_stack}}}$, we get an
  $R_\ms : \dom(\activeReg{\pwfree[W_\var{free\_stack}]}) \fun \MemSeg \times \MemSeg$,
  $\ms_\var{T,free\_stack} = \biguplus_{r \in \dom(\activeReg{\pwfree[W_\var{free\_stack}]})} \pi_2(R_\ms(r))$,
  $\ms_\stk = \biguplus_{r \in \dom(\activeReg{\pwfree[W_\var{free\_stack}]})} \pi_1(R_\ms(r))$,
  $\stkb \in \dom(\ms_\var{T,free\_stack}) \wedge \stkb \in \dom(\ms_\stk)$,
  $\exists R_W : \dom(\activeReg{\pwfree[W_\var{free\_stack}]}) \fun \World\ldotp$
  $W_\var{free\_stack} = \oplus_{r \in \dom(\activeReg{\pwfree[W_\var{free\_stack}]})} R_W(r)$,
  $\forall r \in \activeReg{\pwfree[W_\var{free\_stack}]}$, we have that
  $\npair{R_\ms(r)} \in  \pwfree[W_\var{free\_stack}](r).H \; \xi^{-1}(R_W(r))$.

  We have that $r \in \addressable{\lin, \pwfree} \subseteq \activeReg{\pwfree[W_\var{free\_stack}]}$, so $\npair{R_\ms(r)} \in \pwfree[W_\var{free\_stack}](r).H \; \xi^{-1}(R_W(r))$.
  Because $\pwfree(r).H \nsubeq \stdreg{R(r),\gc}{\pur}.H$ and $W\oplus W_M = W \oplus (W_\var{free\_stack} \oplus W_\var{free\_stack} \oplus W_\var{stack})$ is defined, it follows that also $\pwfree[W_\var{free\_stack}](r).H \nsubeq \stdreg{R(r),\gc}{\pur}.H$.
  This means that also $\npair{R_\ms(r)} \in H^{\mathrm{std}}_{R(r)}\; \xi^{-1}(R_W(r))$.

  From this, it follows that $\dom(R_\ms(r).1) = \dom(R_\ms(r).2) = R(r)$ and we get a $S : R(r) \fun \World$ with $\xi(\xi^{-1}(R_W(r))) = \oplus_{\aaddr \in R(r)} S(\aaddr)$ and $\forall \aaddr \in R(r),n' < n \ldotp \npair[n']{(\ms_\stk(\aaddr),\ms_T(\aaddr))} \in \lrv(S(\aaddr))$.

  Since $\aaddr \in R(r)$ and $n' < n$, we have that $\npair[n']{(\ms_\stk(\aaddr),\ms_T(\aaddr))} \in \lrv(S(\aaddr))$ and
  we can take $W_M' = W_r' \oplus W_{\var{heap}} \oplus (W_{\var{stack}} \oplus W_{\var{free\_stack}}')$ with $W_r' = \oplus_{\aaddr \in (R(r)\setminus \{\aaddr\})} S(\aaddr)$ and $W_\var{free\_stack}' = \oplus_{r' \in (\dom(\activeReg{\pwheap[W_\var{heap}]})\setminus \{r\})} R_W(r')$, and get
  \begin{align*}
    S(\aaddr) \oplus W_M'
    &=S(\aaddr) \oplus (W_r' \oplus W_{\var{free\_stack}}' \oplus (W_{\var{stack}}\oplus W_\var{heap}))\\
    &=
    \oplus_{\aaddr \in R(r)} S(\aaddr) \oplus W_{\var{free\_stack}}' \oplus (W_{\var{stack}}\oplus W_{\var{heap}})\\
    &=
    \xi(\xi^{-1}(R_W(r))) \oplus W_{\var{free\_stack}}' \oplus (W_{\var{stack}} \oplus W_\var{heap})\\
    &=
    R_W(r) \oplus W_{\var{free\_stack}}' \oplus (W_{\var{stack}} \oplus W_\var{heap})\\
    &=
    \oplus_{r \in \dom(\activeReg{\pwheap[W_\var{free\_stack}]})} R_W(r)\oplus (W_{\var{stack}} \oplus W_{\var{heap}})\\
    &=
      W_\var{free\_stack} \oplus (W_{\var{stack}} \oplus W_{\var{heap}})\\
      &= W_M
  \end{align*}

@@

  We have that $\npair{(R_\ms(r).1\update{a}{0},R_\ms(r).2\update{a}{0})} \in \pwfree[W_\var{free\_stack}](r).H \; \xi^{-1}(W_r')$ because $\pwfree[W_\var{free\_stack}](r)$ is address-stratified and $\pwfree[W_\var{free\_stack}](r).H \nsupeq \stdreg{R'(r),\gc}{\pur}.H$.

@@

        From the assumption $\memSat[n''']{\ms^{(3)}_S,\ms^{(3)}_\stk, \stk^{(3)}, \ms^{(3)}_T}{W_M''}$, we know
        \begin{itemize}
        \item $\stk = (\addr + \calllen,\ms_{\priv,S}^{(3)})::(\opc_1,\ms_1):: \dots :: (\opc_m,\ms_m)$
        \item $\ms^{(3)}_S \uplus \ms^{(3)}_\stk \uplus \ms_{\priv,S}^{(3)} \uplus \ms_1 \uplus \dots \uplus \ms_m  \text{ is defined}$
        \item $W''_M = W_{\var{stack}}'' \oplus W_{\var{free\_stack}}'' \oplus W_{\var{heap}}''$
        \item $\ms_\var{T,stack}, \ms_\var{T,free\_stack}, \ms_\var{T,heap}, \ms_{T,f}, \ms_{S,f}, \ms_S',\overline{\sigma}$ such that
          \begin{itemize}
          \item $\ms^{(3)}_S = \ms_{f,S} \uplus \ms_S'$
          \item $\ms^{(3)}_T = \ms_\var{T,stack} \uplus \ms_\var{T,free\_stack} \uplus \ms_\var{T,heap} \uplus \ms_{T,f}$
          \item $\memSatStack{\stk,\ms_\var{T,stack}}{W_{\var{stack}}''}$
          \item $\memSatFStack{\ms^{(3)}_\stk,\ms_\var{T,free\_stack}}{W_{\var{free\_stack}}''}$
          \item $\npair{(\overline{\sigma},\ms_S',\ms_\var{T,heap})} \in \lrheap(\pwheap)(W_{\var{heap}}'')$
          \end{itemize}
        \end{itemize}
        We will pick the same things to show \ref{eq:ftlr:case:last-mem-sat} with a few changes.
        We have to show
        \begin{itemize}
        \item $\Phi_S^{(4)}.\stk = (\opc_1,\ms_1):: \dots :: (\opc_m,\ms_m)$

@@

          By assumption and the fact that the only change is that we moved part of the stack to the free stack.
        \item $\memSatStack{(\opc_1,\ms_1):: \dots :: (\opc_m,\ms_m),\ms_\var{T,stack}\setminus \ms_\var{T,stack} | _{\dom(\ms_{\priv,S}^{(3)})}}{W_{\var{stack}}'''}$

          Follows easily from the private stack satisfaction assumption.
          The distribution functions from the assumption are simply limited to forget about the now revoked region and extend the world partition to be on $W_M'''$, but with the same ownership as in the one we had in the assumption.
          All the new partitions are future worlds of the old ones as none of them owned the revoked region (it was owned by $W_R''$).
        \item $\memSatFStack{\ms^{(3)}_\stk \uplus \ms_{\priv,S}^{(3)},\ms_\var{T,free\_stack} \uplus \ms_\var{T,stack} | _{\dom(\ms_{\priv,S}^{(3)})}}{W_{\var{free\_stack}}'''}$

>>>>

  The property for $\lrheap$, $\memSatFStack{\_,\_}{\_}$, $\memSatStack{\_,\_}{\_}$ follows by their definition from the quantifications over $n' < n$, and the property for $(\_,\_,\_,\_) :_n W$ follows from those.
\end{proof}

\begin{lemma}[Properties of n-equality of worlds]
  \label{lem:n-equality-props}
  If $W_1 \nequal W_2$ then
  \begin{itemize}
  \item $\purePart{W_1} \nequal \purePart{W_2}$
  \item If $W_1' \future W_1$ then there exists a $W_2'$ such that $W_2' \nequal W_1'$ and $W_2' \future W_2$.
  \item If $W_1' \oplus W_1$ is defined, then there exists a $W_2' \nequal W_1'$ and $W_2' \oplus W_2$ is defined.
  \item If $W_1 = W_1' \oplus W_1''$ then there exist $W_2' \nequal W_1'$ and $W_2'' \nequal W_1''$ such that $W_2 = W_2' \oplus W_2''$.
  \item If $W_1' \nequal W_2'$ then $W_1\oplus W_1' \nequal W_2 \oplus W_2'$.
  \item $\xi^{-1}(W_1) \nequal[n-1] \xi^{-1}(W_2)$
  \end{itemize}
\end{lemma}
\begin{proof}
  Easy to prove by unfolding definitions and making unsurprising choices for existentially quantified worlds.
\end{proof}

\begin{lemma}[Non-expansiveness of relations]
  \label{lem:non-expansiveness}
  If $W \nequal W'$, then
  \begin{itemize}
  \item $\readCond{W} \nequal \readCond{W'}$.
  \item If $\stackReadCond{\lin,W} \nequal \stackReadCond{\lin,W'}$.
  \item If $\writeCond{\lin,W} \nequal \writeCond{\lin,W'}$.
  \item If $\stackWriteCond{\lin,W} \nequal \stackWriteCond{\lin,W'}$
  \item If $\xReadCond{W} \nequal \xReadCond{W'}$.
  \item $\lre(W) \nequal \lre(W')$.
  \item $\lrexj(W) \nequal \lrexj(W')$.
  \item If $\execCond{\lin,W} \nequal \execCond{\lin,W'}$.
  \item If $\lrvg{\trust}(W) \nequal \lrvg{\trust}(W')$.
  \item If $\lrrg{\trust}(W) \nequal \lrrg{\trust}(W')$.
  \item If $\memSatFStack{ms_\stk,\ms_T}{W}$, then $\memSatFStack{ms_\stk,\ms_T}{W'}$.
  \item If $\memSatStack{ms_\stk,\ms_T}{W}$, then $\memSatStack{ms_\stk,\ms_T}{W'}$.
  \item If $\npair{(\overline{\sigma},\ms_S,\ms_T)} \in \lrheap{\pwheap}(W)$, then $\npair{(\overline{\sigma},\ms_S,\ms_T)} \in \lrheap{\pwheap[W']}(W')$.
  \item $\memSat{(\ms_S,\stk,\ms_\stk,\ms_T)}{W}$ iff $\memSat{(\ms_S,\stk,\ms_\stk,\ms_T)}{W'}$.
  \end{itemize}
\end{lemma}
\begin{proof}
  The properties for $\readCond{}$, $\stackReadCond{}$, $\writeCond{}$, $\stackWriteCond{}$, $\xReadCond{}$ follow from the fact that these are defined to use the world only for comparing regions using $\nequal$, $\nsubeq$ and $\nsupeq$.

@@

  The property for $\lrv$ follows from the other properties, by definition, from Lemma~\ref{lem:n-equality-props}, and non-expansiveness of regions.

@@

  The property for $\lrheap$, $\memSatFStack{\_,\_}{\_}$, $\memSatStack{\_,\_}{\_}$ and $(\_,\_,\_,\_) :_n W$ follows from the non-expansiveness of regions in the world and Lemma~\ref{lem:n-equality-props}.
\end{proof}

@@

  From $\npair{(\overline{\sigma},\ms_S',\ms_\var{T,heap})} \in \lrheap(W_M)(W_\var{heap})$, we get an
  $R_\ms : \dom(\activeReg{\pwheap[W_\var{heap}]}) \fun \MemSeg \times \MemSeg$,
  $\ms_\var{T,heap} = \biguplus_{r \in \dom(\activeReg{\pwheap[W_\var{heap}]})} \pi_2(R_\ms(r))$,
  $\ms_S = \biguplus_{r \in \dom(\activeReg{\pwheap[W_\var{heap}]})} \pi_1(R_\ms(r))$,
  $\exists R_W : \dom(\activeReg{\pwheap[W_\var{heap}]}) \fun \World\ldotp$
  $W_\var{heap} = \oplus_{r \in \dom(\activeReg{\pwheap[W_\var{heap}]})} R_W(r)$,
  $\forall r \in \activeReg{\pwheap[W_M]}$, we have that
  $\npair[n']{R_\ms(r)} \in  \pwheap[W_\var{heap}](r).H \; \xi^{-1}(R_W(r))$ for all $n' < n$.
  We also get an $R_\var{seal} : \dom(\activeReg{\pwheap}) \fun \powerset{\Seal}$ such that  $\biguplus_{r \in \dom(\activeReg{\pwheap})} R_\var{seal}(r)) \subseteq \overline{\sigma}$ and $\dom(\pwheap(r).H_\sigma) = R_\var{seal}(r)$.

  We have that $r \in \addressable{\lin, \pwheap} \subseteq
  \activeReg{\pwheap[W_\var{heap}]}$, so $\npair[n']{R_\ms(r)} \in
  \pwheap[W_M](r).H \; \xi^{-1}(R_W(r))$.
  Because $\pwheap(r).H \nsubeq \stdreg{R(r),\gc}{\pur}.H$ and $W\oplus W_M$ is defined, it follows that
  also $\pwheap[W_M](r).H \nsubeq \stdreg{R(r),\gc}{\pur}.H$. This
  means that also $\npair[n']{R_\ms(r)} \in
  H^{\mathrm{std}}_{R(r)}\; \xi^{-1}(R_W(r))$.

  From this, it follows that $\dom(R_\ms(r).1) = \dom(R_\ms(r).2) = R(r)$ and we get a $S : R(r) \fun \World$ with $\xi(\xi^{-1}(R_W(r))) = \oplus_{\aaddr \in R(r)} S(\aaddr)$ and $\forall \aaddr \in R(r) \ldotp \npair[n']{(\ms_S(\aaddr),\ms_T(\aaddr))} \in \lrv(S(\aaddr))$.

  Since $\aaddr \in R(r)$, we have that $\npair[n']{(\ms_S(\aaddr),\ms_T(\aaddr))} \in \lrv(S(\aaddr))$ and
  we can take $W_M' = W_r' \oplus W_{\var{heap}}' \oplus (W_{\var{stack}} \oplus W_{\var{free\_stack}})$ with $W_r' = \oplus_{\aaddr \in (R(r)\setminus \{\aaddr\})} S(\aaddr)$ and $W_\var{heap}' = \oplus_{r' \in (\dom(\activeReg{\pwheap[W_\var{heap}]})\setminus \{r\})} R_W(r')$, and get
  \begin{align*}
    S(\aaddr) \oplus W_M'
    &=S(\aaddr) \oplus (W_r' \oplus W_\var{heap}'\oplus (W_{\var{stack}} \oplus W_{\var{free\_stack}}))\\
    &=
    \oplus_{\aaddr \in R(r)} S(\aaddr) \oplus W_{\var{heap}}'\oplus (W_{\var{stack}} \oplus W_{\var{free\_stack}})\\
    &=
    \xi(\xi^{-1}(R_W(r))) \oplus W_\var{heap}'\oplus (W_{\var{stack}} \oplus W_{\var{free\_stack}})\\
    &=
    R_W(r) \oplus W_\var{heap}'\oplus (W_{\var{stack}} \oplus W_{\var{free\_stack}})\\
    &=
    \oplus_{r \in \dom(\activeReg{\pwheap[W_\var{heap}]})} R_W(r)\oplus (W_{\var{stack}} \oplus W_{\var{free\_stack}})\\
    &=
      W_\var{heap} \oplus (W_{\var{stack}} \oplus W_{\var{free\_stack}})\\
      &= W_M
  \end{align*}

@@

  We have that $\npair[n']{(R_\ms(r).1\update{a}{0},R_\ms(r).2\update{a}{0})} \in \pwheap[W_\var{heap}](r).H \; \xi^{-1}(W_r')$ for all $n' < n$ because $\pwheap[W_M](r)$ is address-stratified and $\pwheap[W_M](r).H \nsupeq \stdreg{R'(r),\gc}{\pur}.H$.

@@

  From $\memSatFStack{\ms_\stk,\ms_\var{T,free\_stack}}{W_{\var{free\_stack}}}$, we get an
  $R_\ms : \dom(\activeReg{\pwfree[W_\var{free\_stack}]}) \fun \MemSeg \times \MemSeg$,
  $\ms_\var{T,free\_stack} = \biguplus_{r \in \dom(\activeReg{\pwfree[W_\var{free\_stack}]})} \pi_2(R_\ms(r))$,
  $\ms_\stk = \biguplus_{r \in \dom(\activeReg{\pwfree[W_\var{free\_stack}]})} \pi_1(R_\ms(r))$,
  $\stkb \in \dom(\ms_\var{T,free\_stack}) \wedge \stkb \in \dom(\ms_\stk)$,
  $\exists R_W : \dom(\activeReg{\pwfree[W_\var{free\_stack}]}) \fun \World\ldotp$
  $W_\var{free\_stack} = \oplus_{r \in \dom(\activeReg{\pwfree[W_\var{free\_stack}]})} R_W(r)$,
  $\forall r \in \activeReg{\pwfree[W_\var{free\_stack}]}$, we have that
  $\npair[n']{R_\ms(r)} \in  \pwfree[W_\var{free\_stack}](r).H \; \xi^{-1}(R_W(r))$ for all $n' < n$.

  We have that $r \in \addressable{\lin, \pwfree} \subseteq \activeReg{\pwfree[W_\var{free\_stack}]}$, so $\npair[n']{R_\ms(r)} \in \pwfree[W_\var{free\_stack}](r).H \; \xi^{-1}(R_W(r))$.
  Because $\pwfree(r).H \nsubeq \stdreg{R(r),\gc}{\pur}.H$ and $W\oplus W_M = W \oplus (W_\var{free\_stack} \oplus W_\var{free\_stack} \oplus W_\var{stack})$ is defined, it follows that also $\pwfree[W_\var{free\_stack}](r).H \nsubeq \stdreg{R(r),\gc}{\pur}.H$.
  This means that also $\npair[n']{R_\ms(r)} \in H^{\mathrm{std}}_{R(r)}\; \xi^{-1}(R_W(r))$.

  From this, it follows that $\dom(R_\ms(r).1) = \dom(R_\ms(r).2) = R(r)$ and we get a $S : R(r) \fun \World$ with $\xi(\xi^{-1}(R_W(r))) = \oplus_{\aaddr \in R(r)} S(\aaddr)$ and $\forall \aaddr \in R(r) \ldotp \npair[n']{(\ms_\stk(\aaddr),\ms_T(\aaddr))} \in \lrv(S(\aaddr))$.

  Since $\aaddr \in R(r)$, we have that $\npair[n']{(\ms_\stk(\aaddr),\ms_T(\aaddr))} \in \lrv(S(\aaddr))$ and
  we can take $W_M' = W_r' \oplus W_{\var{heap}} \oplus (W_{\var{stack}} \oplus W_{\var{free\_stack}}')$ with $W_r' = \oplus_{\aaddr \in (R(r)\setminus \{\aaddr\})} S(\aaddr)$ and $W_\var{free\_stack}' = \oplus_{r' \in (\dom(\activeReg{\pwheap[W_\var{heap}]})\setminus \{r\})} R_W(r')$, and get
  \begin{align*}
    S(\aaddr) \oplus W_M'
    &=S(\aaddr) \oplus (W_r' \oplus W_{\var{free\_stack}}' \oplus (W_{\var{stack}}\oplus W_\var{heap}))\\
    &=
    \oplus_{\aaddr \in R(r)} S(\aaddr) \oplus W_{\var{free\_stack}}' \oplus (W_{\var{stack}}\oplus W_{\var{heap}})\\
    &=
    \xi(\xi^{-1}(R_W(r))) \oplus W_{\var{free\_stack}}' \oplus (W_{\var{stack}} \oplus W_\var{heap})\\
    &=
    R_W(r) \oplus W_{\var{free\_stack}}' \oplus (W_{\var{stack}} \oplus W_\var{heap})\\
    &=
    \oplus_{r \in \dom(\activeReg{\pwheap[W_\var{free\_stack}]})} R_W(r)\oplus (W_{\var{stack}} \oplus W_{\var{heap}})\\
    &=
      W_\var{free\_stack} \oplus (W_{\var{stack}} \oplus W_{\var{heap}})\\
      &= W_M
  \end{align*}

@@

  We have that $\npair[n']{(R_\ms(r).1\update{a}{0},R_\ms(r).2\update{a}{0})} \in \pwfree[W_\var{free\_stack}](r).H \; \xi^{-1}(W_r')$ for all $n' < n$ because $\pwfree[W_\var{free\_stack}](r)$ is address-stratified and $\pwfree[W_\var{free\_stack}](r).H \nsupeq \stdreg{R'(r),\gc}{\pur}.H$.

@@

        From the assumption $\memSat[n''']{\ms^{(3)}_S,\ms^{(3)}_\stk, \stk^{(3)}, \ms^{(3)}_T}{W_M''}$, we know
        \begin{itemize}
        \item $\stk = (\addr + \calllen,\ms_{\priv,S}^{(3)})::(\opc_1,\ms_1):: \dots :: (\opc_m,\ms_m)$
        \item $\ms^{(3)}_S \uplus \ms^{(3)}_\stk \uplus \ms_{\priv,S}^{(3)} \uplus \ms_1 \uplus \dots \uplus \ms_m  \text{ is defined}$
        \item $W''_M = W_{\var{stack}}'' \oplus W_{\var{free\_stack}}'' \oplus W_{\var{heap}}''$
        \item $\ms_\var{T,stack}, \ms_\var{T,free\_stack}, \ms_\var{T,heap}, \ms_{T,f}, \ms_{S,f}, \ms_S',\overline{\sigma}$ such that
          \begin{itemize}
          \item $\ms^{(3)}_S = \ms_{f,S} \uplus \ms_S'$
          \item $\ms^{(3)}_T = \ms_\var{T,stack} \uplus \ms_\var{T,free\_stack} \uplus \ms_\var{T,heap} \uplus \ms_{T,f}$
          \item $\memSatStack[n''']{\stk,\ms_\var{T,stack}}{W_{\var{stack}}''}$
          \item $\memSatFStack[n''']{\ms^{(3)}_\stk,\ms_\var{T,free\_stack}}{W_{\var{free\_stack}}''}$
          \item $\npair[n''']{(\overline{\sigma},\ms_S',\ms_\var{T,heap})} \in \lrheap(\pwheap)(W_{\var{heap}}'')$
          \end{itemize}
        \end{itemize}
        We will pick the same things to show \ref{eq:ftlr:case:last-mem-sat} with a few changes.
        We have to show
        \begin{itemize}
        \item $\Phi_S^{(4)}.\stk = (\opc_1,\ms_1):: \dots :: (\opc_m,\ms_m)$

@@

          By assumption and the fact that the only change is that we moved part of the stack to the free stack.
        \item $\memSatStack[n''']{(\opc_1,\ms_1):: \dots :: (\opc_m,\ms_m),\ms_\var{T,stack}\setminus \ms_\var{T,stack} | _{\dom(\ms_{\priv,S}^{(3)})}}{W_{\var{stack}}'''}$

          Follows easily from the private stack satisfaction assumption.
          The distribution functions from the assumption are simply limited to forget about the now revoked region and extend the world partition to be on $W_M'''$, but with the same ownership as in the one we had in the assumption.
          All the new partitions are future worlds of the old ones as none of them owned the revoked region (it was owned by $W_R''$).
        \item $\memSatFStack[n''']{\ms^{(3)}_\stk \uplus \ms_{\priv,S}^{(3)},\ms_\var{T,free\_stack} \uplus \ms_\var{T,stack} | _{\dom(\ms_{\priv,S}^{(3)})}}{W_{\var{free\_stack}}'''}$

          From the $\memSatFStack[n''']{\ms^{(3)}_\stk,\ms_\var{T,free\_stack}}{W_{\var{free\_stack}}''}$ assumption we get $R_\ms : \dom(\activeReg{W_{\var{free\_stack}}''}) \fun \MemSeg \times \MemSeg$ and $R_W : \dom(\activeReg{W_{\var{free\_stack}}''}.\free) \fun \Worlds$ for which
          \begin{itemize}
          \item $\ms^{(3)}_\stk = \biguplus_{r \in \dom(\activeReg{W_{\var{free\_stack}}''.\free})} \pi_1(R_\ms(r))$
          \item $\ms_\var{T,free\_stack} = \biguplus_{r \in \dom(\activeReg{W_{\var{free\_stack}}''.\free})} \pi_2(R_\ms(r))$
          \item $\stkb \in \dom(\ms^{(3)}_\stk)$ and $\stkb \in \dom(\ms_\var{T,free\_stack})$
          \item $W_{\var{free\_stack}}'' \bigoplus_{r \in \dom(\activeReg{W_{\var{free\_stack}}''.\free})} R_W(r)$
          \item $\forall r \in \dom(\activeReg{W_{\var{free\_stack}}''.\free}), n'''' < n'''\ldotp \npair[n'''']{R_\ms(r)} \in W_{\var{free\_stack}}''.\free(r).H \; \xi^{-1}(R_W(r))$
          \end{itemize}
          Now pick
          \[
            R_\ms'(r) =
            \begin{cases}
              (\ms_{\priv,S}^{(3)}|_{\{a'\}} , \ms_\var{T,stack}|_{\{a'\}}) & r_{a'} \in \{r_{b_\stk'}\dots r_{e_\stk'}\}\\
              R_\ms(r) & \totherwise
            \end{cases}
          \]
          and
          \[
            R_W'(r) =
            \begin{cases}
              W'''_{a'} & r_{a'} \in \{r_{b_\stk'}\dots r_{e_\stk'}\} \\
              R_W(r)[\priv.r' \mapsto \revoked,\free.r_{b_\stk'}\dots r_{e_\stk'}\mapsto \stdreg{\{b_\stk'\},\gc}{\spa} \dots \stdreg{\{e_\stk'\},\gc}{\spa}]& \totherwise
            \end{cases}
          \]
          for $W'''_{a'}$ constructed as follows: $W_{\var{stack}}''$ is the part of the world given to the stack judgement in the assumption.
          This world is split into a number of parts to satisfy the memory interpretation of each frame.
          Say $W_{top,\var{stack}}''$ is used for the top stack frame in the assumption.
          The top stack frame is governed by a static region, so by definition it is split into parts that satisfy each of the addresses.
          That is for $a' \in \{b_\stk' \dots e_\stk'\}$, $W_{a'}''$ is the part that makes the value in memory satisfy the value relation.
          Now let $W_{a'}'''$ be $W'''$ but with the ownership of $W_{a'}''$
